Retrofitting Effect Handlers onto OCaml

### 2021-03-12 retro-concurrency.tex
Added file to track changes promised in response

In the operational semantics, the continuations may be resumed more than once.
Captured continuations are copies of the original fibers and resuming the
continuation copies the fibers and leaves the continuation as it is. In our use
cases, continuations will be resumed at-most once, and copying fibers is
unnecessary and inefficient. Instead, Multicore OCaml optimises fibers for
one-shot continuations. Fibers are allocated on the C heap using |malloc| and
are |free|d when the handled computation returns with a value or an exception.
Similar to Farvardin et al.~\cite{Farvardin20}, we use a \emph{stack cache} of
recently freed stacks in order to speed up allocation.

>>>>

In the operational semantics, the continuations may be resumed more than once.
Captured continuations are copies of the original fibers and resuming the
continuation copies the fibers and leaves the continuation as it is. Since our
primary use case is concurrency, continuations will be resumed at-most once, and
copying fibers is unnecessary and inefficient. Instead, Multicore OCaml
optimises fibers for one-shot continuations. Fibers are allocated on the C heap
using |malloc| and are |free|d when the handled computation returns with a value
or an exception. Similar to Farvardin et al.~\cite{Farvardin20}, we use a
\emph{stack cache} of recently freed stacks in order to speed up allocation.
